%%%%%%%  STARTING HERE, Document Formatting Settings


\documentclass[a4,10pt]{article}
\usepackage{latexsym}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}
\usepackage[margin=1cm, top=1cm]{geometry}
\IfFontExistsTF{Source Sans Pro}{%
\setmainfont{Source Sans Pro}
\setsansfont{Source Sans Pro}
}{%
\setmainfont{Latin Modern Roman}
\setsansfont{Latin Modern Sans}
}
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\definecolor{UI_blue}{RGB}{32, 64, 151}
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-13pt} \hrulefill \vspace{-8pt}]
\newcommand{\subtext}[1]{
#1\par\vspace{-0.2cm}}
\setlist[itemize]{align=parleft,left=0pt..1em}
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.65cm}}
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }
\titleformat{\subsection}{\vspace{-0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.2cm}]

%%%%%%%  END OF "Document Formatting Settings" SECTION


\begin{document}

\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \ (+91)-9156011787 \\
            \normalsize \href{mailto:as.anandsumit@gmail.com}{as.anandsumit@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge \underline {SUMIT ANAND}} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{DevOps and Site Reliability Engineer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \normalsize  %Willing to Relocate
            {\href{https://www.linkedin.com/in/asanandsumit/}{linkedin/asanandsumit} } \\
            \href{https://github.com/logtailer}{GitHub/logtailer}
    \end{minipage}   

    {\color{UI_blue} \hrulefill}
\end{center}

Site Reliability Engineer with 4 years of experience adept at developing robust monitoring tools, disaster recovery, and automation solutions. Catalyzing efficiency by transforming operations with strategic automations and ensuring high availability of systems.  %% This can be customized, but I feel this impact statement makes people want to read more.
\vspace{-0.25cm}
\section{Education }

\subsection{M.Tech, Software Systems}
{{\normalsize \normalfont Birla Institute Of Technology and Science - Pilani, RJ} \hfill July 2024 --- July 2026}
\subsection*{B.E, Computer Science Engineering} 
{{\normalsize \normalfont Cambridge Institute Of Technology - Bangalore, KA} \hfill Aug 2018 --- July 2022} 
\vspace{-0.3cm}
\section{Experience}

%%%%%%% ----------------------------------- Role 5 ----------------------------------- %%%%%%%
\subsection*{Software Engineer \hfill Jan 2024 --- Present} 
\subtext{Syncron Software India Pvt. Ltd \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Led zero-downtime cross-account AWS Elastic IP migration for SFTP infrastructure using Python orchestration, staged NLB subnet mapping, Route53 DNS delegation, and rollback utilities.
        \item Designed CloudWatch monitoring and structured JSON logging to cover 15+ failure modes, enabling low-cardinality Prometheus metrics and multi-period alarm evaluation.
        \item Implemented custom sshpiperd SFTP proxy routing in Go and created DNS rollback, EIP detachment, and AZ coverage automation to prevent single-AZ outages.
    \end{zitemize}

%%%%%%% ----------------------------------- Role 5a ----------------------------------- %%%%%%%
\subsection*{Associate Software Engineer - DevOps \hfill Aug 2022 --- Dec 2023} 
\subtext{Syncron Software India Pvt. Ltd \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Built custom AWS Transfer Family auth layer with Lambda and API Gateway replacing legacy SFTP system.
        \item Enhanced CDK/CodePipeline deployment for AWS Data.All using GitHub webhooks and automated releases.
        \item Added GitHub workflow security scans for deprecated packages, reducing risk by 30\%.
        \item Provisioned Terraform for secure business onboarding and automated ECS log rotation for faster fault analysis.
        \item Strengthened EKS with FSx-backed storage and disaster recovery automation, reducing downtime by 90\%.
    \end{zitemize}


%%%%%%% ----------------------------------- Role 4 ----------------------------------- %%%%%%%
\subsection*{DevOps Engineer {\normalsize\normalfont (Intern)} \hfill Apr 2022 --- July 2022} 
\subtext{Syncron Software India Pvt. Ltd \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Launched Lambda function to push Redshift Database metrics to CloudWatch, reducing issue response time by 45\%.
        \item Assisted upgrades for legacy Terraform repositories, achieving a 40\% reduction in deployment time.
    \end{zitemize}

%%%%%%% ----------------------------------- Role 3 ----------------------------------- %%%%%%%
\subsection*{DevOps and Cloud Lead \hfill Sept 2021 --- July 2022} 
\subtext{Google Developers Student Clubs - CIT Bangalore \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Conducted workshops to enhance student knowledge of developer products and platforms by Google, focusing on hands-on experience with Google products. Empowered GDSC members to cultivate new skills collaboratively, growing a community learning environment to frequently engage in creating technical solutions for the communities.
    \end{zitemize}
    

%%%%%%% ----------------------------------- Role 2 ----------------------------------- %%%%%%%
\subsection*{Intern \hfill Dec 2021 --- Apr 2022} 
\subtext{Defence Research Development Organization \hfill Bangalore, KA} 
    \begin{zitemize}
        \item Streamlined recruitment processes by eliminating reliance on third-party agencies for work history verification, ensuring a more efficient and direct hiring process.
        \item Researched and implemented blockchain strategies leading to a remarkable 60\% increase in overall system efficiency and expense reduction. Additionally, successfully halved the processing time for HR transactions by leveraging a distributed network of peers sharing a ledger for employee records.
    \end{zitemize}


\section{Skills}
\textbf{Core:} AWS, Azure, Terraform, Python, Go, Kubernetes, Docker, FastAPI, GitHub Actions | \textbf{Observability:} CloudWatch, Prometheus, Grafana, Loki, Tempo, OpenTelemetry | \textbf{Platform:} ArgoCD, Karpenter, Kyverno, Falco, KEDA, Route53, DynamoDB, KMS, Lambda, SNS, Calico, IRSA
\vspace{-0.25cm}
\section{Certifications}
\begin{tabular}[t]{ p{10em} p{46em}}
\hskills{Dec - 2023} & HashiCorp Certified: Terraform Associate (003) \hfill(\hskills{\href{https://www.credly.com/badges/814918e9-fc9f-4fde-8ea0-5df068b66902}{Credly} }) \\ % 
\hskills{Sept - 2023} & AWS Certified Cloud Practitioner \hfill(\hskills{\href{https://www.credly.com/badges/77765962-e64e-445f-9d74-eb272f5d6923}{Credly} })\\
\end{tabular} 

\end{document}